Development of User-Friendly\\System Identification Techniques

### 2016-03-20 front-and-back-matter/frontmatter.tex
Address some TODOs
Different figure names per chapter
Some small things
Address some minor TODOs

@@

% \TOCInsert{section}{List of Listings}   \lstlistoflistings %TODO: fix this

\printglossary[type=\acronymtype,style=long,toctitle={List of Abbreviations}, title={List of Abbreviations}] %TODO: change format

\glsaddall[types=symbols]
\printglossary[type=symbols,style=altlong4col,title={List of Symbols},toctitle={List of Symbols}]

>>>>

\tikzsetfigurename{frontfig}

@@

\printglossary[type=\acronymtype,style=longheader,toctitle={List of Abbreviations}, title={List of Abbreviations}]

\glsaddall[types=symbols]
\printglossary[type=symbols,style=longheader,title={List of Symbols},toctitle={List of Symbols}]
